Summary Tables ITHIMR

### 2019-05-16 summary_tables_PA_AP.Rmd
emission inventory in one table

@@

trans_share<-c(22.5, 40.0, 22.5, 28.1) 
pm_conc<- c(50, 18, 122, 47 )
city<-cities
shares<- as.data.frame(cbind(city,as.numeric(trans_share), pm_conc))
names(shares)[2]<- "trans_share"
for (x in 1:length(cities))
{
  modes<-names(unlist(io[[cities[x]]]$emission_inventory))
  emissions<-as.data.frame(unlist(io[[cities[x]]]$emission_inventory))
  city_emissions<-cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$emission_inventory)`))
  names(city_emissions)[2]<- "emissions"
  select<- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes<- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)]<- "other"
  summary<-city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2]<- "emissions"
  summary$emissions <- round(summary$emissions*100/sum(summary$emissions), digits=1)
  summary<-as.data.frame(summary)
  summary[nrow(summary)+1,1]<-"Transport share"
  summary[nrow(summary),2]<-as.character(shares$trans_share[x])
  summary[nrow(summary)+1,1]<-"PM2.5 Conc"
  summary[nrow(summary),2]<-as.character(shares$pm_conc[x])
  print(kable(summary, caption= cities[x]))

@@

>>>>

<!-- # Descriptive tables of emission inventory -->

<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->

<!-- trans_share<-c(22.5, 40.0, 22.5, 28.1)  -->
<!-- pm_conc<- c(50, 18, 122, 47 ) -->
<!-- city<-cities -->
<!-- shares<- as.data.frame(cbind(city,as.numeric(trans_share), pm_conc)) -->
<!-- names(shares)[2]<- "trans_share" -->
<!-- for (x in 1:length(cities)) -->
<!-- { -->
<!--   modes<-names(unlist(io[[cities[x]]]$emission_inventory)) -->
<!--   emissions<-as.data.frame(unlist(io[[cities[x]]]$emission_inventory)) -->
<!--   city_emissions<-cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$emission_inventory)`)) -->
<!--   names(city_emissions)[2]<- "emissions" -->
<!--   select<- c("car", "motorcycle", "bus_driver", "truck", "big_truck") -->
<!--   city_emissions$modes<- as.character(city_emissions$modes) -->
<!--   city_emissions$modes[!(city_emissions$modes %in% select)]<- "other" -->
<!--   summary<-city_emissions %>% group_by(modes) %>% summarise(sum(emissions)) -->
<!--   names(summary)[2]<- "emissions" -->
<!--   summary$emissions <- round(summary$emissions*100/sum(summary$emissions), digits=1) -->
<!--   summary<-as.data.frame(summary) -->
<!--   summary[nrow(summary)+1,1]<-"Transport share" -->
<!--   summary[nrow(summary),2]<-as.character(shares$trans_share[x]) -->
<!--   summary[nrow(summary)+1,1]<-"PM2.5 Conc" -->
<!--   summary[nrow(summary),2]<-as.character(shares$pm_conc[x]) -->
<!--   print(kable(summary, caption= cities[x])) -->

<!-- } -->

<!-- ``` -->

@@

trans_share<-c(22.5, 40.0, 22.5, 28.1) 
pm_conc<- c(50, 18, 122, 47 )
city<-cities
shares<- as.data.frame(cbind(city,as.numeric(trans_share), pm_conc))
names(shares)[2]<- "trans_share"
for (x in 1:length(cities))
{
  modes<-names(unlist(io[[cities[x]]]$emission_inventory))
  emissions<-as.data.frame(unlist(io[[cities[x]]]$emission_inventory))
  city_emissions<-cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$emission_inventory)`))
  names(city_emissions)[2]<- "emissions"
  select<- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes<- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)]<- "other"
  summary<-city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2]<- cities[x]
  summary[[cities[x]]] <- round(summary[[cities[x]]]*100/sum(summary[[cities[x]]]), digits=1)
  summary<-as.data.frame(summary)
  summary[nrow(summary)+1,1]<-"Transport share"
  summary[nrow(summary),2]<-as.character(shares$trans_share[x])
  summary[nrow(summary)+1,1]<-"PM2.5 Conc"
  summary[nrow(summary),2]<-as.character(shares$pm_conc[x])
  io[[cities[x]]]$summary_emission<- summary

@@

summary_all<- cbind(io[[cities[1]]]$summary_emission,io[[cities[2]]]$summary_emission,io[[cities[3]]]$summary_emission,io[[cities[4]]]$summary_emission)
summary_all<- summary_all[-c(3,5,7)]
summary_all$modes[2]<- "bus"

print(kable(summary_all))
```
